%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\cvsection{Personal Project}
\cvsectionIcon{Personal Projects}{\faCogs}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
    \cventry
    {Accident Data CRUD App} % Description
    {ExtraMile Website} % Project name
    {\href{https://github.com/giathuan123/extramile}{\faGithubSquare}} % Code
    {Stack | \diExpressOriginal \diReactPlainWordmark \diNodejsPlain \diPythonPlain } % Stack(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Designed and developed a CRUD web application that processed over 5,000,000 data points. }
        \item{Worked with teammates to design an interactive React.js frontend to display processed json.}
        \item{Designed and implemented RESTful backend server using Express.js to serve processed json to the frontend. }
        \item{Wrote internal Python scripts to wrangle 5Gb of data to reduce initial load on server to 300Mb300Mb300Mb }
        \item{Designed and implemented a custom indexing and caching data structure by leveraging javascript dictionaries that improved load time from 32 seconds to under 5 seconds, and improve querying time from 3s to under a second while ensuring data consistency across indexes. }
        \item{Improved teammates' developement experience by writing internal documentation to facilitate communication amongst teammates. }
        \end{cvitems}
    }
    \cventry
    {Database Management System} % Description
    {Car Service Database Interface} % Project name
    {\href{https://github.com/giathuan123/cs166-project}{\faGithubSquare}} % Code
    {Stack | \diJavaPlain \diPostgresqlPlain } % Stack(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Designed ERD diagrams using LucidChart to improve clarity during developement. }
        \item{Designed and implemented a CRUD desktop application for a car servicing dataset with over 140,000 datapoints across 5 entities. }
        \item{Implemented database schema in PostgresSQL database with automated insertion triggers. }
        \item{Designed and implemented GUI using JavaSwing to interact with PostgresSQL database. }
        \end{cvitems}
    }
    \cventry
    {Data Visualizer} % Description
    {Shopee Delivery HeatMap} % Project Name
    {\href{https://github.com/giathuan123/HeatMap}{\faGithubSquare}} % Code
    {Stack | \diExpressOriginal \diNodejsPlain \diBootstrapPlain \diJqueryPlain \diPythonPlain } % Stack(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item{Designed, developed and deployed a heat map data visualization web application using the MVC design pattern. }
          \item{Wrote a csv parser in Python using pandas to parse uploaded data sheets into json for data visualization. }
          \item{Designed RESTful backend server using flask and SQLite enabling persistent storage of data sets. }
          \item{Designed and developed frontend using bootstrap and Jquery.js to create an interative web application. }
        \end{cvitems}
    }
    \cventry
    {Web Scrapper} % Description
    {Lazada Price Getter} % Project name
    {Github} % Code
    {Stack | \diNodejsPlain } % Stack(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed an automated web scrapper cli program to scrape Lazada.com for product and vendor information using Puppeteer.js and scraped over 3,000 products and 50 vendors }
        \end{cvitems}
    }
\end{cventries}
